Four reasons your build is slow

### 2019-01-17 paper.tex
cites

\section{Analysis tool}
\label{sec:analysis}
In this section we describe the tools we use to analyse make builds, diagnose problems related
to parallelism, and identify places for improvement. In section \ref{sec:makeanalysis} we
discuss the modified version of GNU Make \cite{gnumake4.2} we use to record enough information about a
project's build to reconstruct the build graph during a post-mortem analysis.
In section \ref{sec:straceinstr} we discuss how we use a slightly modified version of strace to
record all of the system calls made during the project's build and then use the system calls
to determine the real dependencies of the build. In section \ref{sec:revisegraphs} we discuss
how to combine the information from these two tools to transform a build graph into
a new graph with potentially more parallelism.

@@

To collect the desired level of information from a run of GNU Make \cite{gnumake4.2}, we run it with the
debug level of 'verbose', use our own wrappers, which print additional information, and use
a modified version of make which prints directory and timing information for each shell command run.
All of this information is written to a file and later used to reconstruct
the build graph of a successful build.  The reconstructed graph contains all of the shell commands
executed during the build as well as the time each one took to complete.  With the structure of the
build and the timing information the work and span of the build can be calculated. Work is the total
time to execute every shell command in the build graph, and span is the longest time to execute any
sequence of shell commands which must execute sequentially.  For example, the span of a single
make rule is, the longest time to execute a dependency plus the sum of the times to execute each
recipe.  Parallelism is defined as \begin{math} \frac{span}{work} \end{math}, therefore to increase
the parallelism of a project the span must be decreased; making span an important place to focus
performance improvements.

>>>>

\section{Analysis tool}
\label{sec:analysis}
In this section we describe the tools we use to analyse make builds, diagnose problems related
to parallelism, and identify places for improvement. In section \ref{sec:makeanalysis} we
discuss the modified version of GNU Make \cite{gnumakemanual} we use to record enough information about a
project's build to reconstruct the build graph during a post-mortem analysis.
In section \ref{sec:straceinstr} we discuss how we use a slightly modified version of strace to
record all of the system calls made during the project's build and then use the system calls
to determine the real dependencies of the build. In section \ref{sec:revisegraphs} we discuss
how to combine the information from these two tools to transform a build graph into
a new graph with potentially more parallelism.

@@

To collect the desired level of information from a run of GNU Make \cite{gnumakemanual}, we run it with the
debug level of 'verbose', use our own wrappers, which print additional information, and use
a modified version of make which prints directory and timing information for each shell command run.
All of this information is written to a file and later used to reconstruct
the build graph of a successful build.  The reconstructed graph contains all of the shell commands
executed during the build as well as the time each one took to complete.  With the structure of the
build and the timing information the work and span of the build can be calculated. Work is the total
time to execute every shell command in the build graph, and span is the longest time to execute any
sequence of shell commands which must execute sequentially.  For example, the span of a single
make rule is, the longest time to execute a dependency plus the sum of the times to execute each
recipe.  Parallelism is defined as \begin{math} \frac{span}{work} \end{math}, therefore to increase
the parallelism of a project the span must be decreased; making span an important place to focus
performance improvements.
